The Strong Gravitational Lens Finding Challenge

### 2018-02-16 paper.tex
Added authors.
Update on Overleaf.

\author{
R. Benton Metcalf \inst{1,2}\thanks{E-mail: robertbenton.metcalf@unibo.it} 
\and
M. Meneghetti \inst{2}
\and
Camille Avestruz \inst{3,4,5}\fnmsep\thanks{Provost's Postdoctoral Scholar at the University of Chicago}
\and
Fabio Bellagamba\inst{1}
\and
Cl\'ecio R. Bom\inst{6,7}
\and
Emmanuel Bertin\inst{8}
\and
R\'emi Cabanac \inst{9}
\and
Etienne Decenci\`ere \inst{10}
\and
R\'emi Flamary \inst{11}
\and
Raphael Gavazzi \inst{8}
\and
Mario Geiger \inst{12} 
\and
Philippa Hartley \inst{13}
\and
Marc Huertas-Company \inst{14}
\and
Neal Jackson \inst{13}
\and
Eric Jullo \inst{15}
\and
Jean-Paul Kneib \inst{12}
\and
L\'{e}on V. E. Koopmans \inst{16}
\and
Fran\c{c}ois Lanusse \inst{17}
\and
Chun-Liang Li \inst{18}
\and
Quanbin Ma \inst{18}
\and
Martin Makler \inst{7}
\and
Nan Li \inst{19}
\and
Matthew Lightman \inst{15}
\and
Carlo Enrico Petrillo \inst{16}
\and
Christoph Sch\"{a}fer \inst{12}
\and
Alessandro Sonnenfeld \inst{21}
\and
Amit Tagore \inst{13}
\and
Crescenzo Tortora \inst{16}
\and
Diego Tuccillo \inst{10,14}
\and
Manuel B. Valent\'in \inst{7}
\and
Santiago Velasco-Forero \inst{10}
\and
Gijs A. Verdoes Kleijn \inst{16}
\and
Georgios Vernardos \inst{16}
}

\institute{
Departimento di Fisica \& Astronomia, Universit\`a di Bologna, via Gabetti 93/2, 4012 Bologna, Italy 
\and
INAF-Osservatorio Astronomico di Bologna, via Ranzani 1, 40127 Bologna, Italy 
\and
Enrico Fermi Institute, The University of Chicago, Chicago, IL 60637 U.S.A.
\and
Kavli Institute for Cosmological Physics, The University of Chicago, Chicago, IL 60637 U.S.A.
\and
Department of Astronomy \& Astrophysics, The University of Chicago, Chicago, IL 60637 U.S.A.
\and
Centro Federal de Educa\c{c}\~ao Tecnol\'ogica Celso Suckow da Fonseca, CEP 23810-000,  Itagua\'i, RJ, Brazil
\and
Centro Brasileiro de Pesquisas F\'isicas, CEP 22290-180, Rio de Janeiro, RJ, Brazil
\and
Institut d'Astrophysique de Paris, Sorbonne Universit\'e, CNRS,  UMR 7095, 98 bis bd Arago, 75014 Paris, France.
\and
IRAP, Universit\'e de Toulouse, CNRS, UPS, Toulouse, France.
\and
MINES Paristech, PSL Research University, Centre for Mathematical Morphology, 35 rue  Saint-Honore, Fontainebleau, France
\and
Laboratoire Lagrange, Universi\'{e} de Nice Sophia-Antipolis, Centre National de la Recherche Scientifique,
\and
Institute of Physics, Laboratory of Astrophysics, Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL),  Observatoire de Sauverny, 1290 Versoix, Switzerland 
\and
Jodrell Bank Centre for Astrophysics, School of Physics \& Astronomy, University of  Manchester, Oxford Rd, Manchester M13 9PL, UK Observatoire de la C\^{o}te d'Azur, Parc Valrose, 06108 Nice, France 
\and
LERMA, Observatoire de Paris, CNRS, Universit\'e Paris Diderot, 61, Avenue de l'Observatoire F-75014, Paris, France
\and
Aix Marseille Universit\'e, CNRS, LAM (Laboratoire d'Astrophysique de Marseille) UMR 7326, 13388, Marseille, France
\and
Kapteyn Astronomical Institute, University of Groningen, Postbus 800, 9700 AV, Groningen, The Netherlands
\and
McWilliams Center for Cosmology, Department of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA
\and
School of Computer Science, Carnegie Mellon University, Pittsburgh, PA 15213, USA
\and
School of Physics and Astronomy, Nottingham University, University Park, Nottingham, NG7 2RD, UK
\and
JPMorgan Chase, Chicago, IL 60603 U.S.A.
\and
Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan
}

%\date{Accepted . Received ; in original form }
%\maketitle
%\label{firstpage}

@@

\begin{table*}
\centering
\begin{tabular}{rlll}
  \hline
 & Name & type & authors \\ 
  \hline
  1 & AstrOmatic & Space-Based & Bertin   \\ 
  2 & GAHEC IRAP & Space-Based & Cabanac  \\ 
  3 & CAS Swinburne Melb$^\dagger$& Ground-Based & Jacobs   \\ 
  4 & ALL-star & Ground-Based & Avestruz, N. Li \& Lightman  \\ 
  5 & Manchester1 & Space-Based & Jackson \& Tagore  \\ 
  6 & CMU-DeepLens-Resnet-Voting & Space-Based & Ma, Lanusse \& C. Li  \\ 
  7 & Manchester SVM & Ground-Based & Hartley \& Flamary  \\ 
  8 & CMU-DeepLens-ResNet & Space-Based & Francois Lanusse, Ma, C. Li \& Ravanbakhsh \\ 
  9 & CMU-DeepLens-Resnet-Voting & Ground-Based & Ma, Lanusse \& C. Li   \\ 
  10 & YattaLensLite & Space-Based &  Sonnenfeld  \\ 
  11 & NeuralNet2$^\dagger$ & Space-Based &  Davies  \\ 
  12 & CAST & Ground-Based &  Roque De Bom, Valent\'{\i}n \&  Makler  \\ 
  13 & CMU-DeepLens-ResNet-ground3 & Ground-Based &  Lanusse, Ma, Ravanbakhsh \& C. Li \\ 
  14 & GAMOCLASS & Space-Based &  Huertas-Company, Tuccillo, Velasco-Forero \& Decenci\`{e}re \\ 
  15 & LASTRO EPFL (CNN) & Space-Based & Geiger, Sch\"{a}fer \& Kneib \\ 
  16 & Manchester SVM & Space-Based &  Hartley  \& Flamary\\ 
  17 & CMU-DeepLens-ResNet-aug & Space-Based & Ma,  Lanusse, Ravanbakhsh \& C. Li \\ 
  18 & LASTRO EPFL & Ground-Based & Geiger, Sch\"{a}fer \& Kneib   \\ 
  19 & CAST & Space-Based & Bom, Valent\'{\i}n \& Makler  \\ 
  20 & AstrOmatic & Ground-Based & Bertin  \\ 
  21 & All-now & Space-Based & Avestruz, N. Li \& Lightman   \\ 
  22 & Manchester-NA2 & Ground-Based & Jackson \& Tagore  \\ 
  23 & YattaLensLite & Ground-Based & Sonnenfeld   \\ 
  24 & Kapteyn Resnet & Space-Based & Petrillo, Tortora, Verdoes Kleijn, Koopmans \& Vernardos \\ 
   \hline
   & & &$\dagger$ No description was submitted for this paper.
\end{tabular}
\caption{Entries to the challenges.}
\label{table:entries}
\end{table*}

@@

>>>>

\author{
R. Benton Metcalf \inst{1,2}\thanks{E-mail: robertbenton.metcalf@unibo.it} 
\and
M. Meneghetti \inst{2}
\and
Camille Avestruz \inst{3,4,5}\fnmsep\thanks{Provost's Postdoctoral Scholar at the University of Chicago}
\and
Fabio Bellagamba\inst{1}
\and
Cl\'ecio R. Bom\inst{6,7}
\and
Emmanuel Bertin\inst{8}
\and
R\'emi Cabanac \inst{9}
\and
Andrew Davies \inst{22}
\and
Etienne Decenci\`ere \inst{10}
\and
R\'emi Flamary \inst{11}
\and
Raphael Gavazzi \inst{8}
\and
Mario Geiger \inst{12} 
\and
Philippa Hartley \inst{13}
\and
Marc Huertas-Company \inst{14}
\and
Neal Jackson \inst{13}
\and
Eric Jullo \inst{15}
\and
Jean-Paul Kneib \inst{12}
\and
L\'{e}on V. E. Koopmans \inst{16}
\and
Fran\c{c}ois Lanusse \inst{17}
\and
Chun-Liang Li \inst{18}
\and
Quanbin Ma \inst{18}
\and
Martin Makler \inst{7}
\and
Nan Li \inst{19}
\and
Matthew Lightman \inst{15}
\and
Carlo Enrico Petrillo \inst{16}
\and
Stephen Serjeant \inst{22}
\and
Christoph Sch\"{a}fer \inst{12}
\and
Alessandro Sonnenfeld \inst{21}
\and
Amit Tagore \inst{13}
\and
Crescenzo Tortora \inst{16}
\and
Diego Tuccillo \inst{10,14}
\and
Manuel B. Valent\'in \inst{7}
\and
Santiago Velasco-Forero \inst{10}
\and
Gijs A. Verdoes Kleijn \inst{16}
\and
Georgios Vernardos \inst{16}
}

\institute{
Departimento di Fisica \& Astronomia, Universit\`a di Bologna, via Gabetti 93/2, 4012 Bologna, Italy 
\and
INAF-Osservatorio Astronomico di Bologna, via Ranzani 1, 40127 Bologna, Italy 
\and
Enrico Fermi Institute, The University of Chicago, Chicago, IL 60637 U.S.A.
\and
Kavli Institute for Cosmological Physics, The University of Chicago, Chicago, IL 60637 U.S.A.
\and
Department of Astronomy \& Astrophysics, The University of Chicago, Chicago, IL 60637 U.S.A.
\and
Centro Federal de Educa\c{c}\~ao Tecnol\'ogica Celso Suckow da Fonseca, CEP 23810-000,  Itagua\'i, RJ, Brazil
\and
Centro Brasileiro de Pesquisas F\'isicas, CEP 22290-180, Rio de Janeiro, RJ, Brazil
\and
Institut d'Astrophysique de Paris, Sorbonne Universit\'e, CNRS,  UMR 7095, 98 bis bd Arago, 75014 Paris, France.
\and
IRAP, Universit\'e de Toulouse, CNRS, UPS, Toulouse, France.
\and
MINES Paristech, PSL Research University, Centre for Mathematical Morphology, 35 rue  Saint-Honore, Fontainebleau, France
\and
Laboratoire Lagrange, Universi\'{e} de Nice Sophia-Antipolis, Centre National de la Recherche Scientifique,
\and
Institute of Physics, Laboratory of Astrophysics, Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL),  Observatoire de Sauverny, 1290 Versoix, Switzerland 
\and
Jodrell Bank Centre for Astrophysics, School of Physics \& Astronomy, University of  Manchester, Oxford Rd, Manchester M13 9PL, UK Observatoire de la C\^{o}te d'Azur, Parc Valrose, 06108 Nice, France 
\and
LERMA, Observatoire de Paris, CNRS, Universit\'e Paris Diderot, 61, Avenue de l'Observatoire F-75014, Paris, France
\and
Aix Marseille Universit\'e, CNRS, LAM (Laboratoire d'Astrophysique de Marseille) UMR 7326, 13388, Marseille, France
\and
Kapteyn Astronomical Institute, University of Groningen, Postbus 800, 9700 AV, Groningen, The Netherlands
\and
McWilliams Center for Cosmology, Department of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA
\and
School of Computer Science, Carnegie Mellon University, Pittsburgh, PA 15213, USA
\and
School of Physics and Astronomy, Nottingham University, University Park, Nottingham, NG7 2RD, UK
\and
JPMorgan Chase, Chicago, IL 60603 U.S.A.
\and
Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan
\and
School of Physical Sciences, The Open University, Walton Hall, Milton Keynes, MK7 6AA, UK
}

@@

\begin{table*}
\centering
\begin{tabular}{rlll}
  \hline
 & Name & type & authors \\ 
  \hline
  1 & AstrOmatic & Space-Based & Bertin   \\ 
  2 & GAHEC IRAP & Space-Based & Cabanac  \\ 
  3 & CAS Swinburne Melb$^\dagger$& Ground-Based & Jacobs   \\ 
  4 & ALL-star & Ground-Based & Avestruz, N. Li \& Lightman  \\ 
  5 & Manchester1 & Space-Based & Jackson \& Tagore  \\ 
  6 & CMU-DeepLens-Resnet-Voting & Space-Based & Ma, Lanusse \& C. Li  \\ 
  7 & Manchester SVM & Ground-Based & Hartley \& Flamary  \\ 
  8 & CMU-DeepLens-ResNet & Space-Based & Francois Lanusse, Ma, C. Li \& Ravanbakhsh \\ 
  9 & CMU-DeepLens-Resnet-Voting & Ground-Based & Ma, Lanusse \& C. Li   \\ 
  10 & YattaLensLite & Space-Based &  Sonnenfeld  \\ 
  11 & NeuralNet2 & Space-Based &  Davies  \\ 
  12 & CAST & Ground-Based &  Roque De Bom, Valent\'{\i}n \&  Makler  \\ 
  13 & CMU-DeepLens-ResNet-ground3 & Ground-Based &  Lanusse, Ma, Ravanbakhsh \& C. Li \\ 
  14 & GAMOCLASS & Space-Based &  Huertas-Company, Tuccillo, Velasco-Forero \& Decenci\`{e}re \\ 
  15 & LASTRO EPFL (CNN) & Space-Based & Geiger, Sch\"{a}fer \& Kneib \\ 
  16 & Manchester SVM & Space-Based &  Hartley  \& Flamary\\ 
  17 & CMU-DeepLens-ResNet-aug & Space-Based & Ma,  Lanusse, Ravanbakhsh \& C. Li \\ 
  18 & LASTRO EPFL & Ground-Based & Geiger, Sch\"{a}fer \& Kneib   \\ 
  19 & CAST & Space-Based & Bom, Valent\'{\i}n \& Makler  \\ 
  20 & AstrOmatic & Ground-Based & Bertin  \\ 
  21 & All-now & Space-Based & Avestruz, N. Li \& Lightman   \\ 
  22 & Manchester-NA2 & Ground-Based & Jackson \& Tagore  \\ 
  23 & YattaLensLite & Ground-Based & Sonnenfeld   \\ 
  24 & Kapteyn Resnet & Space-Based & Petrillo, Tortora, Verdoes Kleijn, Koopmans \& Vernardos \\ 
   \hline
   & & &$\dagger$ No description was submitted for this paper.
\end{tabular}
\caption{Entries to the challenges.}
\label{table:entries}
\end{table*}

@@

\subsubsection{NeuralNet2 (Davies, Serjeant) }

Our lens finder included wavelet prefiltering. The image was convolved with the Mallat wavelet with a kernel size of 4 in both the horizontal and vertical directions, then combined and compared to the original image to make the final image; $final image = \sqrt[]{H^{2}+V^{2}}$. This prefiltering was performed the emphasise the edges in the images, improving the results from the Convolutional Neural Network (CNN). The CNN had 2 convolution layers each containing 32 $3\times3$ filters, incorporating dropout and max-pooling, and then 3 dense fully-connected layers to classify each image. The network was trained on 18000 of the 20000 training images; training took 15 epochs and was completed once the validation loss was minimised. The training was validated on the remaining 2000 images. Validation loss $\mathcal{L}(\theta)$ was calculated using binary cross entropy
\begin{equation}
\mathcal{L}(\theta) = \sum_{i=1}^{n} \big[ y_{i}$ $log(p_{i}) + (1 $ - $ y_{i})$ $log(1 $ - $ p_{i}) \big]
\end{equation} where $\mathcal{L}(\theta)$ is the loss function, $n$ is the number of inputs, $y_{i}$ is the true value of the $i^{th}$ input , and $p_{i}$ is the predicted value for the $i^{th}$ input from the network. A perfect loss of $0$ was generated once every predicted value matched the true value for every input. The network was made and trained in Python 2.7 using the open-source libraries \textsc{theano} and \textsc{keras}\footnote{\href{https://github.com/keras-team/keras}{\tt https://github.com/keras-team/keras}}. A more developed version of our lens finder will appear in Davies, Bromley and Serjeant (in preparation).
